\documentclass[10pt, a4paper]{article}

% Preamble
\usepackage{xcolor}
\usepackage{pagecolor}
\usepackage{geometry} % For page margins
\usepackage{fontspec}
% \geometry{a4paper, margin=1in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{lipsum} % For filler text
\usepackage{changepage} %For Indenting
\usepackage{graphicx}

% Page settings
\pagecolor{white}
\color{black}
\setmainfont{TeX Gyre Termes}

% Margins
\geometry{
  top=1cm,
  bottom=2.5cm,
  left=1.4cm,
  right=1.4cm
}

% Sections style
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{0em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
\newenvironment{subs} %Indenting
  {\adjustwidth{2em}{0pt}}
  {\endadjustwidth}
  
% Commands
\renewcommand{\labelitemi}{\scalebox{1}{$\bullet$}}  


\begin{document}
\begin{center}
\textbf{Johnny Teichter}\\
\texttt{Gothenburg|(+46)722127856|teichohn@gmail.com}
\end{center}
\section*{EDUCATION}
\texttt{}\\[-0.5cm]
\textbf{IT Högskolan} \hfill Stockholm, Remote\\
\noindent\makebox[\textwidth][r]{May 2026}\\
\textit{Higher Vocational Degree in Penetration Testing}

\section*{EXPERIENCE}
\texttt{}\\[-0.5cm]
\textbf{Enclave AB} \hfill Stockholm, Remote\\
\noindent\makebox[\textwidth][r]{October 2025 - May 2026}\\
\textit{Infrastructure Lead Developer}\\
\begin{itemize}[leftmargin=0.3cm, itemsep=0.1cm]
\item Building a single node air-gapped Kubernetes cluster of cloud native applications.
\item Used helm template to set up and customise Vault, Gitlab CE, Nextcloud AIO, VLLM and more.
\item Decided the methods to use for dev team, made a project plan and set goals + milestones.
\item Researched AI Assisted clusters and wrote maintenance scripts for the environment.
\end{itemize}
\texttt{}\\[-0.2cm]
\textbf{Mekonomen Group} \hfill Östersund, Jämtland\\
\noindent\makebox[\textwidth][r]{March 2024 - April 2024}\\
\textit{Customers Service Agent}\\
\begin{itemize}[leftmargin=0.3cm, itemsep=0.1cm]
\item Intern due to hiring stop, answered on emails three hours per day and was assigned internal portal studies the rest.
\item Found critical vulnerabilities in the portal and reported them to the team. 
\end{itemize}
\texttt{}\\[-0.2cm]
\textbf{Alina Service} \hfill Östersund, Jämtland\\
\noindent\makebox[\textwidth][r]{January 2024}\\
\textit{Technical Repair Shop Assistant}\\
\begin{itemize}[leftmargin=0.3cm, itemsep=0.1cm]
\item Trial work week in role selection process. Did memtest, refurbish of hardware, software reinstallations/updates/fixes + cashier work. 
\end{itemize}
\texttt{}\\[-0.2cm]
\textbf{OneForma} \hfill Östersund, Remote\\
\noindent\makebox[\textwidth][r]{2023}\\
\textit{Search Engine Result Analyst}\\
\begin{itemize}[leftmargin=0.3cm, itemsep=0.1cm]
\item Analysing data bulks from Google and Bing engines and ranking results based on relevance and locality of the queries. 
\end{itemize}
\texttt{}\\[-0.5cm]
\section*{SKILLS \& CERTIFICATIONS}
\texttt{}\\[-0.5cm]
\textbf{Skills:} C, C++, Python, JavaScript, Bash, AI Agentics, NodeJS + React, HTML, CSS, YAML, TeX, XML\\
\textbf{Certifications:} freeCodeCamp Javascript Algorithms and Data Structures
\end{document}
